Simulations

### 2025-12-05 simulations.qmd
updates

  # Run the 100,000 tournament sims in parallel
  sim_list <- future_lapply(
    X = 1:100000,
    FUN = function(rep) {
      simulate_single_elimination_tournament(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        series = series,
        third_place = third_place,
        reseeded = reseeded,
        seeding_structure = seeding_structure
      )
    },
    future.seed = TRUE   # parallel-safe RNG
  )

@@

  # Run 100,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:100000,
    FUN = function(rep) {
      simulate_double_elimination_tournament(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        series = series,
        final = final,
        seeding_structure = seeding_structure
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

@@

@@

  # Run 100,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:1000000,
    FUN = function(rep) {
      simulate_roundrobin_r(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        r = r
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

@@

  # Run 100,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:100000,
    FUN = function(rep) {
      simulate_group_stage_tournament(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        rounds = rounds,
        group_length = group_length
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

@@

  # Run 100,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:100000,
    FUN = function(rep) {
      simulate_step_ladder(
        num_teams = teams,
        distribution = distribution,
        series = series,
        seeding_structure = seeding_structure
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

@@

  return(plot_df)
}
```

@@

  # Validate input
  valid_structures <- c("singleElimination", "doubleElimination", "roundRobin", "groupStage", "stepLadder")
  if (!tournament_structure %in% valid_structures) {
    stop(paste("Invalid tournament_structure. Must be one of:", 
               paste(valid_structures, collapse = ", ")))
  }

@@

@@

@@

compute_and_store_mi_by_tournament("singleElimination")
compute_and_store_mi_by_tournament("doubleElimination")
compute_and_store_mi_by_tournament("roundRobin")
compute_and_store_mi_by_tournament("groupStage")
compute_and_store_mi_by_tournament("stepLadder")

all_mi <- bind_rows(
  singleElimination_mi,
  doubleElimination_mi,
  groupStage_mi,
  roundRobin_mi,
  stepLadder_mi
)
```

@@

```{r}
combined_plot_df <- plot_mi(all_mi, c(
  "singleElimination_normal_noTies_1",
  "singleElimination_uniform_noTies_1", 
  "singleElimination_same_noTies_1", 
  #"singleElimination_exponential_noTies_1",
  "doubleElimination_normal_noTies_1", 
  "doubleElimination_uniform_noTies_1",
  "doubleElimination_same_noTies_1", 
  #"doubleElimination_exponential_noTies_1", 
  "roundRobin_normal_noTies_1", 
  "roundRobin_uniform_noTies_1", 
  "roundRobin_same_noTies_1", 
  #"roundRobin_exponential_noTies_1", 
  "groupStage_normal_noTies_1_4groups",
  "groupStage_uniform_noTies_1_4groups",
  "groupStage_same_noTies_1_4groups"#,
  #"groupStage_exponential_noTies_1_4groups"
  )
)

@@

print(combined_plot)
```

@@

# Display plots
print(single_elimination_noties_plot)
print(single_elimination_ties_plot)
```

@@

```{r}
double_elimination_plot_df <- plot_mi(doubleElimination_mi)

@@

@@

  # Check for badseed (could be fifth or sixth part)
  bad_seeding <- ifelse(any(parts == "badseed"), "Bad Seed", "Good Seed")

  return(data.frame(
    distribution = distribution,
    ties = ties,
    series = series,
    #final = final,
    bad_seeding = bad_seeding
  ))
}

# Add parameter columns to the plot data
double_elimination_plot_df <- double_elimination_plot_df %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    series = factor(series, levels = c(1, 3, 7)),
    # Create a label for the additional parameters
    param_label = paste(bad_seeding, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
double_elimination_plot_df <- double_elimination_plot_df %>%
  mutate(
    color_group = paste(bad_seeding, sep = " | ")
  )

@@

@@

@@

@@

@@

@@

>>>>

  # Run the 10,000 tournament sims in parallel
  sim_list <- future_lapply(
    X = 1:10000,
    FUN = function(rep) {
      simulate_single_elimination_tournament(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        series = series,
        third_place = third_place,
        reseeded = reseeded,
        seeding_structure = seeding_structure
      )
    },
    future.seed = TRUE   # parallel-safe RNG
  )

@@

  # Run 10,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:10000,
    FUN = function(rep) {
      simulate_double_elimination_tournament(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        series = series,
        final = final,
        seeding_structure = seeding_structure
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

@@

### Repechege

```{r}
repechege_param_grid <- expand.grid( 
  distribution = c("Normal","Uniform", "Same", "Exponential"), 
  ties = c(FALSE, TRUE), 
  series = c(1, 3, 7), 
  bad_seeding_structure = c(FALSE, TRUE) 
  )

repechege_run_sim_block <- function(
  teams, distribution, ties, series, bad_seeding_structure, p_block) {

  # Build key
    # Build the key
  parts <- c(
    "Repechage",
    tolower(distribution),
    ifelse(ties, "ties", "noTies"),
    paste0(series),
    if (bad_seeding_structure) "badseed"
  )

  # Run 10,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:10000,
    FUN = function(rep) {
      simulate_repechege_tournament(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        series = series,
        seeding_structure = seeding_structure
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

with_progress({
  p_block <- progressor(steps = nrow(repechege_param_grid))

  for (i in seq_len(nrow(repechege_param_grid))) {
    row <- repechege_param_grid[i, ]

    repechege_run_sim_block(
      teams        = teams,
      distribution = row$distribution,
      ties         = row$ties,
      series       = row$series,
      bad_seeding_structure = row$bad_seeding_structure,
      p_block = p_block
    )
  }
})
```

@@

  # Run 10,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:5000,
    FUN = function(rep) {
      simulate_roundrobin_r(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        r = r
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

@@

  # Run 10,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:10000,
    FUN = function(rep) {
      simulate_group_stage_tournament(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        rounds = rounds,
        group_length = group_length
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

@@

  # Run 10,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:10000,
    FUN = function(rep) {
      simulate_step_ladder(
        num_teams = teams,
        distribution = distribution,
        series = series,
        seeding_structure = seeding_structure
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

@@

  return(plot_df)
}

compute_mut_plots_combinations <- function(dataset) {

  num_teams <- teams

  results <- numeric(num_teams)

  for (k in 1:num_teams) {
    df <- dataset %>%
      mutate(
        true_rank = ifelse(true_rank <= k, 1, true_rank),
        rank_hat = ifelse(rank_hat <= k, 1, rank_hat)
      )
    binary_vector <- c(rep(1, k), rep(0, num_teams - k))
    results[k] <- mut_info(df, num_teams, binary_vector)
  }
  return(results)
}

@@

  # Validate input
  valid_structures <- c("singleElimination", "doubleElimination", "roundRobin", "groupStage", "stepLadder", "Repechage")
  if (!tournament_structure %in% valid_structures) {
    stop(paste("Invalid tournament_structure. Must be one of:", 
               paste(valid_structures, collapse = ", ")))
  }

@@

  repechege_key <- function(row, type) {
    c(
      type,
      tolower(row$distribution),
      ifelse(row$ties, "ties", "noTies"),
      paste0(row$series),
      if (row$bad_seeding_structure) "badseed"
    )
  }

@@

   if (tournament_structure %in% c("Repechage")) {
    result <- process_tournament_type("Repechage", 
                                      repechege_param_grid, 
                                      repechege_key)
    results_list$Repechege <- result
  }

@@

compute_and_store_mi_by_tournament("singleElimination")
compute_and_store_mi_by_tournament("doubleElimination")
compute_and_store_mi_by_tournament("roundRobin")
compute_and_store_mi_by_tournament("groupStage")
compute_and_store_mi_by_tournament("stepLadder")
compute_and_store_mi_by_tournament("Repechage")

all_mi <- bind_rows(
  singleElimination_mi,
  doubleElimination_mi,
  groupStage_mi,
  roundRobin_mi,
  stepLadder_mi,
  Repechage_mi
)

all_mi_combinations <- bind_rows(
  singleElimination_combinations_mi,
  doubleElimination_combinations_mi,
  groupStage_combinations_mi,
  roundRobin_combinations_mi,
  stepLadder_combinations_mi,
  Repechage_combinations_mi
)
```

@@

```{r}
combined_plot_df <- plot_mi(all_mi, c(
  "singleElimination_normal_noTies_1",
  "singleElimination_uniform_noTies_1", 
  "singleElimination_same_noTies_1", 
  "singleElimination_exponential_noTies_1",
  "doubleElimination_normal_noTies_1", 
  "doubleElimination_uniform_noTies_1",
  "doubleElimination_same_noTies_1", 
  "doubleElimination_exponential_noTies_1", 
  "roundRobin_normal_noTies_1", 
  "roundRobin_uniform_noTies_1", 
  "roundRobin_same_noTies_1", 
  "roundRobin_exponential_noTies_1", 
  "groupStage_normal_noTies_1_4groups",
  "groupStage_uniform_noTies_1_4groups",
  "groupStage_same_noTies_1_4groups",
  "groupStage_exponential_noTies_1_4groups"
  )
)

@@

combined_combinations_df <- plot_mi(all_mi_combinations, c(
  "singleElimination_normal_noTies_1",
  "singleElimination_uniform_noTies_1", 
  "singleElimination_same_noTies_1", 
  "singleElimination_exponential_noTies_1",
  "doubleElimination_normal_noTies_1", 
  "doubleElimination_uniform_noTies_1",
  "doubleElimination_same_noTies_1", 
  "doubleElimination_exponential_noTies_1", 
  "roundRobin_normal_noTies_1", 
  "roundRobin_uniform_noTies_1", 
  "roundRobin_same_noTies_1", 
  "roundRobin_exponential_noTies_1", 
  "groupStage_normal_noTies_1_4groups",
  "groupStage_uniform_noTies_1_4groups",
  "groupStage_same_noTies_1_4groups",
  "groupStage_exponential_noTies_1_4groups"
  )
)

combined_combinations_df <- combined_combinations_df %>%
  select(-any_of(c("tournament_type", "distribution", "group_length"))) %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name_combined(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    # Create a label for the additional parameters
    param_label = paste(tournament_type, sep = "\n")
  )

combined_combinations_df <- combined_combinations_df %>%
  mutate(
    color_group = case_when(
      tournament_type == "groupStage" ~ "groupStage (4 Groups)",
      TRUE ~ tournament_type
    )
  )

combined_combinations_plot <- ggplot(combined_combinations_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    ~ distribution,
    labeller = labeller(
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Mutual Information (No Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 7),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 2))

print(combined_plot)
print(combined_combinations_plot)
```

@@

# Combine the combination datasets
single_elimination_combinations_plot_df <- bind_rows(
  plot_mi(singleElimination_combinations_mi),
  plot_mi(stepLadder_combinations_mi)
)

# Add parameter columns to the plot data
single_elimination_combinations_plot_df <- single_elimination_combinations_plot_df %>%
  select(-any_of(c("tournament_type", "distribution", "ties", "series", "third_place", "reseeded", "bad_seeding", "param_label", "color_group"))) %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name_se(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  filter(third_place == "Third Place" | tournament_type == "stepLadder") %>% 
  mutate(
    series = factor(series, levels = c(1, 3, 7)),
    # Create a label for the additional parameters
    param_label = paste(tournament_type, reseeded, bad_seeding, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
single_elimination_combinations_plot_df <- single_elimination_combinations_plot_df %>%
  mutate(
    color_group = paste(tournament_type, reseeded, bad_seeding, sep = " | ")
  )

# Filter data for No Ties
single_elim_combinations_noties_df <- single_elimination_combinations_plot_df %>%
  filter(ties == "No Ties")

# Filter data for Ties
single_elim_combinations_ties_df <- single_elimination_combinations_plot_df %>%
  filter(ties == "Ties")

# Plot 1: No Ties (Combinations)
single_elimination_combinations_noties_plot <- ggplot(single_elim_combinations_noties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Series:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Single Elimination (Combinations): Mutual Information (No Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Parameters"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 7),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 2))

# Plot 2: Ties (Combinations)
single_elimination_combinations_ties_plot <- ggplot(single_elim_combinations_ties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Series:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Single Elimination (Combinations): Mutual Information (Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Parameters"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 7),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 2))

# Display plots
print(single_elimination_noties_plot)
print(single_elimination_ties_plot)

# Display plots
print(single_elimination_combinations_noties_plot)
print(single_elimination_combinations_ties_plot)

@@

```{r}
double_elimination_plot_df <- bind_rows(
  plot_mi(doubleElimination_mi),
  plot_mi(Repechage_mi)
)

@@

  if (tournament_type == "doubleElimination"){
    # Extract ties (third part)
    ties <- ifelse(parts[3] == "ties", "Ties", "No Ties")

@@

    # Check for badseed (could be fifth or sixth part)
    bad_seeding <- ifelse(any(parts == "badseed"), "Bad Seed", "Good Seed")
  } else if (tournament_type == "Repechage"){
    # Extract ties (third part)
    ties <- ifelse(parts[3] == "ties", "Ties", "No Ties")

    # Check for badseed (could be fifth or sixth part)
    bad_seeding <- ifelse(any(parts == "badseed"), "Bad Seed", "Good Seed")
  }

  return(data.frame(
    tournament_type = tournament_type,
    distribution = distribution,
    ties = ties,
    series = series,
    #final = final,
    bad_seeding = bad_seeding
  ))
}

# Add parameter columns to the plot data
double_elimination_plot_df <- double_elimination_plot_df %>%
  select(-any_of(c("tournament_type", "distribution", "ties", "series", "bad_seeding", "param_label", "color_group"))) %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    series = factor(series, levels = c(1, 3, 7)),
    # Create a label for the additional parameters
    param_label = paste(tournament_type, bad_seeding, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
double_elimination_plot_df <- double_elimination_plot_df %>%
   mutate(
    color_group = paste(tournament_type, bad_seeding, sep = " | ")
  )

@@

double_elimination_combinations_plot_df <- bind_rows(
  plot_mi(doubleElimination_combinations_mi),
  plot_mi(Repechage_combinations_mi)
)

  if (tournament_type == "doubleElimination"){
    # Extract ties (third part)
    ties <- ifelse(parts[3] == "ties", "Ties", "No Ties")

    # Check for badseed (could be fifth or sixth part)
    bad_seeding <- ifelse(any(parts == "badseed"), "Bad Seed", "Good Seed")
  } else if (tournament_type == "Repechage"){
    # Extract ties (third part)
    ties <- ifelse(parts[3] == "ties", "Ties", "No Ties")

    # Check for badseed (could be fifth or sixth part)
    bad_seeding <- ifelse(any(parts == "badseed"), "Bad Seed", "Good Seed")
  }

  return(data.frame(
    tournament_type = tournament_type,
    distribution = distribution,
    ties = ties,
    series = series,
    #final = final,
    bad_seeding = bad_seeding
  ))
}

# Add parameter columns to the plot data
double_elimination_combinations_plot_df <- double_elimination_combinations_plot_df %>%
  select(-any_of(c("tournament_type", "distribution", "ties", "series", "bad_seeding", "param_label", "color_group"))) %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    series = factor(series, levels = c(1, 3, 7)),
    # Create a label for the additional parameters
    param_label = paste(tournament_type, bad_seeding, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
double_elimination_combinations_plot_df <- double_elimination_combinations_plot_df %>%
   mutate(
    color_group = paste(tournament_type, bad_seeding, sep = " | ")
  )

# Filter data for No Ties
double_elimination_combinations_plot_noTies_df <- double_elimination_combinations_plot_df %>%
  filter(ties == "No Ties")

# Filter data for Ties
double_elimination_combinations_plot_ties_df <- double_elimination_combinations_plot_df %>%
  filter(ties == "Ties")

# Plot 1: No Ties (Combinations)
double_elimination_combinations_noties_plot <- ggplot(double_elimination_combinations_plot_noTies_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Double Elimination (Combinations): Mutual Information (No Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Seeding"
  ) +
  scale_y_continuous(limits = c(0.25, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

# Plot 2: Ties (Combinations)
double_elimination_combinations_ties_plot <- ggplot(double_elimination_combinations_plot_ties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Double Elimination (Combinations): Mutual Information (Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Seeding"
  ) +
  scale_y_continuous(limits = c(0.25, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

@@

# Display plots
print(double_elimination_combinations_noties_plot)
print(double_elimination_combinations_ties_plot)

@@

roundRobin_combinations_plot_df <- plot_mi(roundRobin_combinations_mi)

# Add parameter columns to the plot data
roundRobin_combinations_plot_df <- roundRobin_combinations_plot_df %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    series = factor(rounds, levels = c(1, 2, 4)),
  )

# Filter data for No Ties
roundRobin_combinations_plot_noties_df <- roundRobin_combinations_plot_df %>%
  filter(ties == "No Ties")

# Filter data for Ties
roundRobin_combinations_plot_ties_df <- roundRobin_combinations_plot_df %>%
  filter(ties == "Ties")

# Plot 1: No Ties (Combinations)
roundRobin_combinations_noties_plot <- ggplot(roundRobin_combinations_plot_noties_df, aes(x = index, y = mi_values, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Round Robin (Combinations): Mutual Information (No Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20")

# Plot 2: Ties (Combinations)
roundRobin_combinations_ties_plot <- ggplot(roundRobin_combinations_plot_ties_df, aes(x = index, y = mi_values, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Round Robin (Combinations): Mutual Information (Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20")

@@

# Display plots
print(roundRobin_combinations_noties_plot)
print(roundRobin_combinations_ties_plot)

@@

group_stage_combinations_plot_df <- plot_mi(groupStage_combinations_mi)

# Add parameter columns to the plot data
group_stage_combinations_plot_df <- group_stage_combinations_plot_df %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    series = factor(rounds, levels = c(1, 2, 4)),
    # Create a label for the additional parameters
    param_label = paste(group_length, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
group_stage_combinations_plot_df <- group_stage_combinations_plot_df %>%
  mutate(
    color_group = paste(group_length, sep = " | ")
  )

# Filter data for No Ties
group_stage_combinations_noties_df <- group_stage_combinations_plot_df %>%
  filter(ties == "No Ties")

# Filter data for Ties
group_stage_combinations_ties_df <- group_stage_combinations_plot_df %>%
  filter(ties == "Ties")

# Plot 1: No Ties (Combinations)
group_stage_combinations_noties_plot <- ggplot(group_stage_combinations_noties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Group Stage (Combinations): Mutual Information (No Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Group Length:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

# Plot 2: Ties (Combinations)
group_stage_combinations_ties_plot <- ggplot(group_stage_combinations_ties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Group Stage (Combinations): Mutual Information (Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Group Length:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

@@

# Display plots
print(group_stage_combinations_noties_plot)
print(group_stage_combinations_ties_plot)
